\documentclass{beamer}
\usetheme{Madrid}

\title{Overcooked}
\author{Davide Luccioli}
\institute{University of Bologna}
\date{}

\begin{document}

\begin{frame}{Project Overview}
  \begin{columns}
    \column{0.5\textwidth}
    \textbf{Objective}
    \begin{itemize}
      \item To train robust agents for the Overcooked-AI environment using Multi-Agent Proximal Policy Optimization (MAPPO).
      \item Focus on generalization across different layouts and partner behaviors.
    \end{itemize}
    \vfill

    \column{0.5\textwidth}
    \textbf{Methodology}
    \begin{itemize}
      \item Implemented a MAPPO agent with a centralized critic.
      \item \textbf{Multi-Layout Training}: Agent trained on a random selection of layouts.
      \item \textbf{Partner Generalization}: Agent trained with a stochastic partner to improve adaptability.
    \end{itemize}
  \end{columns}
\end{frame}

\begin{frame}{Key Results \& Findings}
  \textbf{Single Layout Performance}
  \begin{itemize}
    \item Agents successfully mastered individual layouts, with emergent specialized strategies observed in layouts like \texttt{asymmetric\_advantages}.
  \end{itemize}
  
  \textbf{Multi-Layout Generalization}
  \begin{itemize}
    \item The agent performed well on layouts it was trained on and showed some generalization to structurally similar unseen layouts.
    \item Failed to generalize to more complex, fundamentally different layouts.
  \end{itemize}
  
  \textbf{Partner Generalization}
  \begin{itemize}
    \item Training with a stochastic partner forced the agent to learn more robust strategies.
    \item On layouts encouraging specialization (e.g., \texttt{asymmetric\_advantages}), the agent struggled to adapt, showing that overcoming ingrained strategies is a major challenge.
  \end{itemize}
\end{frame}
  
\begin{frame}{Conclusion}
  \begin{itemize}
    \item MAPPO is effective for learning cooperative tasks in Overcooked.
    \item Layout Generalization is Limited: While agents can adapt to structurally similar unseen layouts, they struggle with fundamentally different ones, indicating some overfitting.
    \item Agents can be trained to handle unpredictable partners, but this often comes at the cost of optimal performance in layouts that require tight, specialized coordination.
  \end{itemize}
\end{frame}

\end{document}
